An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-23 paper.tex
Start to redescribe BFS

\begin{defn}
A \textbf{temporal path} of length $m$ on an evolving graph $G_n$
from temporal node $(v_1, t_1)$ to temporal node $(v_m, t_m)$} is
a time-ordered sequence of active nodes,
$\langle (v_1, t_1), (v_2, t_2), \ldots, (v_m, t_m) \rangle$.
Here, time ordering means that $t_1 \leq t_2 \leq \cdots \leq t_m$ and
$v_i = v_j$ iff $t_i \ne t_j$.
\end{defn}

@@

\begin{algorithm}[h]
 \SetKwFor{For}{for}{}{end}
 \SetKwFor{While}{while}{}{end}
 \SetKwFor{If}{if}{}{end}
 \SetKwFunction{nei}{forward-neighbors}
 \SetKwFunction{enqueue}{enqueue}
 \SetKwProg{Fn}{function}{}{end}
 \Fn{BFS($G_n, (s,t)$)}{
  $dict.(s,t) = 0$ \\
  $i = 1$ \\
  $fronter = \emptyset$ \\
  \enqueue{$frontier, (s,t)$} \\
 \While{$frontier \ne \emptyset$}{
   $next = \emptyset$ \\
   \For{$(u,t') \in frontier$}{
     \For{$(v,t'') \in$\nei{$(u,t')$}}{
          \If{$(v,t'') \notin d$}{
              $dict.(v,t'') = i$\\
              \enqueue{$next, (v,t'')$}
              }
         }
       }
  $frontier = next$ \\
  $i = i+1$ \\
  }
  \textbf{return} $dict$
}
 \caption{Breadth-first search (BFS) on an evolving graph: given
$G_n$, an evolving graph represented by adjacency lists, and a root $(s, t)$,

 is a node
of $G_n$.
For each node-time stamp pair $(v_i,t_i)$,
we use a dictionary $dict.(v_i,t_i)$ to store its distance (the length of temporal
paths) from $(s, t)$. We also use
two first-in, first-out queue $frontier$ and $next$, where $frontier$
stores the frontier nodes of the current discovered regions and $next$ stores
the frontier nodes of the next level.
The algorithm returns $dict$ which stores all reachable node-time stamp pairs from $(s,t)$ such that if $dict.(v_i, t_i) = k$,
the length of the shortest temporal path
from $(s,t)$ to $(v_i, t_i)$ is $k$.}
 \label{alg:bfs}
\end{algorithm}

>>>>

\begin{defn}
A \textbf{temporal path} of length $m$ on an evolving graph $G_n$
from temporal node $(v_1, t_1)$ to temporal node $(v_m, t_m)$ is
a time-ordered sequence of active nodes,
$\langle (v_1, t_1), (v_2, t_2), \ldots, (v_m, t_m) \rangle$.
Here, time ordering means that $t_1 \leq t_2 \leq \cdots \leq t_m$ and
$v_i = v_j$ iff $t_i \ne t_j$.
\end{defn}

@@

For each temporal node $(v_i,t_i)$, we use a dictionary $dict.(v_i,t_i)$
to store its distance from $(s, t)$. We also use
two FIFO queues $frontier$ and $next$, where $frontier$
stores the frontier nodes of the current discovered regions and $next$ stores
the frontier nodes of the next level.

\begin{algorithm}[h]
 \SetKwFor{For}{for}{}{end}
 \SetKwFor{While}{while}{}{end}
 \SetKwFor{If}{if}{}{end}
 \SetKwFunction{nei}{forward-neighbors}
 \SetKwFunction{enqueue}{enqueue}
 \SetKwProg{Fn}{function}{}{end}
 \Fn{BFS($G_n, (s,t)$)}{
  $dict.(s,t) = 0$ \\
  $i = 1$ \\
  $fronter = \emptyset$ \\
  \enqueue{$frontier, (s,t)$} \\
 \While{$frontier \ne \emptyset$}{
   $next = \emptyset$ \\
   \For{$(u,t') \in frontier$}{
     \For{$(v,t'') \in$\nei{$(u,t')$}}{
          \If{$(v,t'') \notin d$}{
              $dict.(v,t'') = i$\\
              \enqueue{$next, (v,t'')$}
              }
         }
       }
  $frontier = next$ \\
  $i = i+1$ \\
  }
  \textbf{return} $dict$
}
\caption{Breadth-first search (BFS) on an evolving graph: given
$G_n$, an evolving graph represented by adjacency lists, and a root $(s, t)$.
The algorithm returns $dict$ which stores all reachable node-time stamp pairs from $(s,t)$ such that if $dict.(v_i, t_i) = k$,
the length of the shortest temporal path
from $(s,t)$ to $(v_i, t_i)$ is $k$.
}
\label{alg:bfs}
\end{algorithm}
